Full 18s Community composition

### 2020-01-11 code/exploratory/whole_18s_community_compare.Rmd
major reorg

```{r output, include=F}
dir.create(here("manuscript/figs/S5_18s"))
ggsave(filename = here("manuscript/figs/S5_18s/18s_rel_abund.pdf"), plot=rel_abund_phyla)
```

>>>>

```{r output, include=F}
dir.create(here("manuscript/figs/S5_18s"))
# ggsave(filename = here("manuscript/figs/S5_18s/18s_rel_abund.pdf"), plot=rel_abund_phyla)
```
